\pkg{plotROC}: A Better Tool for Plotting ROC Curves

### 2015-02-02 Paper/sachs2015plotROC.Rmd
Submitted to JSS

An interactive ROC plot can be exported by using the `export_interactive_roc` function, which returns a character string containing the necessary \proglang{HTML} and \proglang{JavaScript}. The character string can be copy-pasted into an html document, or better yet, incorporated directly into a dynamic document using \pkg{knitr} [@knitr]. In a \pkg{knitr} document, it is necessary to use the `cat` function on the results and use the chunk option `results = 'asis'` so that the interactive plot is displayed correctly. For documents that contain multiple interactive plots, it is necessary to assign each plot a unique name using the `prefix` argument of `export_interactive_roc`. This is necessary to ensure that the \proglang{JavaScript} code manipulates the correct svg elements. For examples of interactive plots and how to incorporate them into \pkg{knitr} documents, see the package vignette (`vignette("examples", package = "plotROC")`) or the web page https://sachsmc.github.io/plotROC/. The next code block shows an example \pkg{knitr} chunk that can be used in an .Rmd document to display an interactive plot.

```{r int-no, results = 'asis', eval = FALSE, verbatim = TRUE}
cat(
  export_interactive_roc(single.rocplot, 
                        prefix = "a")
  )
```

@@

This manuscript is completely reproducible using the source files available at http://github.com/sachsmc/plotROC-paper. The output below indicates the \proglang{R} packages and versions used. Compiling the pdf output also requires `pandoc` version 1.13.1 and `pdflatex`.

>>>>

An interactive ROC plot can be exported by using the `export_interactive_roc` function, which returns a character string containing the necessary \proglang{HTML} and \proglang{JavaScript}. The character string can be copy-pasted into an html document, or better yet, incorporated directly into a dynamic document using \pkg{knitr} [@knitr]. In a \pkg{knitr} document, it is necessary to use the `cat` function on the results and use the chunk options `results = 'asis'` and `fig.keep = 'none'` so that the interactive plot is displayed correctly. For documents that contain multiple interactive plots, it is necessary to assign each plot a unique name using the `prefix` argument of `export_interactive_roc`. This is necessary to ensure that the \proglang{JavaScript} code manipulates the correct svg elements. For examples of interactive plots and how to incorporate them into \pkg{knitr} documents, see the package vignette (`vignette("examples", package = "plotROC")`) or the web page https://sachsmc.github.io/plotROC/. The next code block shows an example \pkg{knitr} chunk that can be used in an .Rmd document to display an interactive plot.

```{r int-no, results = 'asis', fig.keep = 'none', eval = FALSE, verbatim = TRUE}
cat(
  export_interactive_roc(single.rocplot, 
                        prefix = "a")
  )
```

@@

This manuscript is completely reproducible using the source files. The output below indicates the \proglang{R} packages and versions used. Compiling the pdf output also requires `pandoc` version 1.13.1 and `pdflatex`.

### 2015-02-02 Paper/sachs2015plotROC.tex
Submitted to JSS

An interactive ROC plot can be exported by using the
\texttt{export\_interactive\_roc} function, which returns a character
string containing the necessary \proglang{HTML} and
\proglang{JavaScript}. The character string can be copy-pasted into an
html document, or better yet, incorporated directly into a dynamic
document using \pkg{knitr} \citep{knitr}. In a \pkg{knitr} document, it
is necessary to use the \texttt{cat} function on the results and use the
chunk option \texttt{results = \textquotesingle{}asis\textquotesingle{}}
so that the interactive plot is displayed correctly. For documents that
contain multiple interactive plots, it is necessary to assign each plot
a unique name using the \texttt{prefix} argument of
\texttt{export\_interactive\_roc}. This is necessary to ensure that the
\proglang{JavaScript} code manipulates the correct svg elements. For
examples of interactive plots and how to incorporate them into
\pkg{knitr} documents, see the package vignette
(\texttt{vignette("examples", package = "plotROC")}) or the web page
https://sachsmc.github.io/plotROC/. The next code block shows an example
\pkg{knitr} chunk that can be used in an .Rmd document to display an
interactive plot.

\begin{verbatim}
```{r int-no, results = 'asis'}
cat(
  export_interactive_roc(single.rocplot, 
                        prefix = "a")
  )
```
\end{verbatim}

@@

This manuscript is completely reproducible using the source files
available at http://github.com/sachsmc/plotROC-paper. The output below
indicates the \proglang{R} packages and versions used. Compiling the pdf
output also requires \texttt{pandoc} version 1.13.1 and
\texttt{pdflatex}.

>>>>

An interactive ROC plot can be exported by using the
\texttt{export\_interactive\_roc} function, which returns a character
string containing the necessary \proglang{HTML} and
\proglang{JavaScript}. The character string can be copy-pasted into an
html document, or better yet, incorporated directly into a dynamic
document using \pkg{knitr} \citep{knitr}. In a \pkg{knitr} document, it
is necessary to use the \texttt{cat} function on the results and use the
chunk options
\texttt{results = \textquotesingle{}asis\textquotesingle{}} and
\texttt{fig.keep = \textquotesingle{}none\textquotesingle{}} so that the
interactive plot is displayed correctly. For documents that contain
multiple interactive plots, it is necessary to assign each plot a unique
name using the \texttt{prefix} argument of
\texttt{export\_interactive\_roc}. This is necessary to ensure that the
\proglang{JavaScript} code manipulates the correct svg elements. For
examples of interactive plots and how to incorporate them into
\pkg{knitr} documents, see the package vignette
(\texttt{vignette("examples", package = "plotROC")}) or the web page
https://sachsmc.github.io/plotROC/. The next code block shows an example
\pkg{knitr} chunk that can be used in an .Rmd document to display an
interactive plot.

\begin{verbatim}
```{r int-no, results = 'asis', fig.keep = 'none'}
cat(
  export_interactive_roc(single.rocplot, 
                        prefix = "a")
  )
```
\end{verbatim}

@@

This manuscript is completely reproducible using the source files. The
output below indicates the \proglang{R} packages and versions used.
Compiling the pdf output also requires \texttt{pandoc} version 1.13.1
and \texttt{pdflatex}.
